Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Add an author

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}} \\

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\

%%% Fill in address here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road} \\

%%% Fill in city and country here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.)} \\

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com}
}

>>>>

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\

%%% Fill in address here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\

%%% Fill in city and country here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com}
}
